Simulation with algorithm 2

### 2021-08-05 supplementary/simulation-alogorithm2/sim_setup_algo2.Rmd
added sim design small iteration

# Five iterations of each design (changing seeds)

@@

hc = stats::hclust(dist(comp))
groups <- cutree(hc, k=5) %>% as_tibble() %>% bind_cols(comp) %>% 
  mutate(value = as.character(value))
library(RColorBrewer)
library(scales)
groups %>% ggplot(aes(x=PC1, y = PC2)) + geom_point(aes(color = value)) +
  scale_color_brewer(palette = "Dark2") + theme_bw()
```

>>>>

@@

hc = stats::hclust(dist(comp))
groups <- cutree(hc, k=koptimal) %>% as_tibble() %>% bind_cols(comp) %>% 
  mutate(value = as.character(value))
library(RColorBrewer)
library(scales)
groups %>% ggplot(aes(x=PC1, y = PC2)) + geom_point(aes(color = value)) +
  scale_color_brewer(palette = "Dark2") + theme_bw()
```
